\section{Proposed Methods}
Our algorithm is based on the Group Steiner Tree problem \cite{reich1989beyond, garg:ja00}, and it and involves the following steps:
\begin{enumerate}
\item
Sample $G_i=(V, E_i)$ subgraphs of $G$, $i=1,\ldots,N'$, where $N'=O(n^2)$, where each $E_i$ is obtained
by picking each edge $e\in E$ independently with probability $p$. Let $\G=\{G_1,\ldots,G_{N'}\}$ denote the set of samples.
\item
Let $\comp(G_i)$ denote the set of connected components in $G_i$
\item
Let $\comp=\cup_i \comp(G_i)$ denote the set of all the components, considered as a multiset
\item
We solve the following variant of the Group Steiner Tree problem, which we call max cover GST: find a tree $T$ in $G$ with
$|T|\leq k$ such that $\sum_{C\in\comp, C\cap T\neq\phi} |C|$ is maximized
\begin{enumerate}
\item
As in \cite{garg:ja00}, we sample a tree $H$ from a tree metric on $G$, and run the Max cover GST algorithm
in Section \ref{sec:max-cover-gst} to find a tree $T$ in $H$. We transform $T$ to a tree $T'$ in $G$,
with polylog increase in cost
\end{enumerate}
\end{enumerate}

For a sampled graph $G_i$, let $\inf(T, G_i)=\sum_{C\in \comp(G_i), C\cap T\neq\emptyset} |C|$. Let $\sinf(T, \G)=\frac{1}{N'}\sum_i \inf(T, G_i)$.

\begin{lemma}
\label{lemma:conc}
If $N'\geq 3n^2/\epsilon^2$, for every set $S\subseteq V$, we have 
\[
\sinf(S, \G)\in[(1-\epsilon)\einf(S,G), (1+\epsilon)\einf(S, G)],
\]
with high probability.
\end{lemma}
\begin{proof}
By definition, we have $\einf(S, G)=E[\inf(S, G_i)]$, where the expectation is over the sampled graphs $G_i\in\G$. We have
\[
N'\frac{\sinf(S,\G)}{n} = \sum_{i=1}^{N'} \frac{\inf(S, G_i)}{n}
\]

Further, for any $S\neq\emptyset$, we have $\frac{\inf(S, G_i)}{n}\in [\frac{1}{n}, 1]$. By the Chernoff bound, we have
\begin{eqnarray*}
\Pr[N'\cdot\sinf(S,\G)\not\in[(1-\epsilon)N'\cdot\einf(S, G), (1+\epsilon)N'\cdot\einf(S, G)]] &\leq& 2 exp(-\frac{N'\cdot\einf(S, G)\epsilon^2}{3n})\\
&\leq& 2 exp(-n\cdot\einf(S, G))\\
&\leq& 2 e^{-n},
\end{eqnarray*}
since $N'\geq 3n^2/\epsilon^2$ and $\einf(S, G)\geq 1$, if $S\neq\emptyset$.

Since the number of non-empty sets $S$ is $2^n-1$, the probability that there exists any set $S$ satisfying the above condition is at most $2\cdot 2^n \cdot e^{-n}\leq 1/(e/2)^{n-1}$.
\end{proof}

Let $\hat{T}=\text{argmax}_T \sinf(T,\G)$ 
be an optimal solution for the sampled set $\G$, and let $T^*=\text{argmax}_T \einf(T, G)$ be an optimal solution with the maximum expected influence.

\begin{lemma}
\label{lemma:saa}
Suppose $T$ is a solution satisfying 
$\sinf(T, \G)\geq \alpha\cdot \sinf(\hat{T}, \G)$. Then
$\einf(T)\geq\frac{1-\epsilon}{1+\epsilon}\alpha\cdot\einf(T^*)$, with high probability, where $\G$ is the set of $N$ sampled subgraphs.
\end{lemma}
\begin{proof}
With high probability, we have
\begin{eqnarray*}
\einf(T, G) &\geq& \frac{1}{1+\epsilon}\sinf(T,\G) \mbox{, by Lemma \ref{lemma:conc}}\\
&\geq& \frac{\alpha}{1+\epsilon} \sinf(\hat{T}, G)\\
&\geq& \frac{\alpha}{1+\epsilon} \sinf(T^*, G) \mbox{, by definition of $\hat{T}$}\\
&\geq& \alpha\frac{1-\epsilon}{1+\epsilon}\einf(T^*,G) \mbox{, by Lemma \ref{lemma:conc}}
\end{eqnarray*}

\end{proof}

\subsection{Max cover GST}
\label{sec:max-cover-gst}

Let $H=(V, E)$ be a tree rooted at node $r$, which is constructed using a tree  embedding corresponding to $G$. Let $\G=\{G_1,\ldots,G_{N'}\}$ denote a set of $N'$ sampled subgraphs, as before, and let $\comp=\{C_1,\ldots,C_N\}$ be a multi-set of components from the sampled subgraphs $G_i\in\G$. 
Following earlier definitions, $\sinf(T,\G)=\frac{1}{N'}\sum_{C\in\comp, C\cap T\neq\emptyset} |C|$.
Let $\hat{T}$ and $T^*$ be as in Lemma \ref{lemma:saa}, and let 
$OPT=\sinf(\hat{T},\G)$. 
Let $\compl = \{C\in\comp: |C|\in[2^{\ell}, 2^{\ell+1})\}$.
Let $OPT^{(\ell)}=\frac{1}{N'}\sum_{C\in\compl, C\cap T\neq\emptyset} |C|$

We consider the following sub-problem here.

\noindent
\textbf{Problem.}
The objective is to find a tree $T$ in $H$ such that
\begin{eqnarray*}
|T| &\leq& k\\
\sum_{C\in\comp, C\cap T\neq\phi} |C| &=& OPT \mbox{ is maximized}
\end{eqnarray*}

We consider the following linear program, denoted by $LP_1^{(\ell)}$:

\begin{eqnarray}
\nonumber
\max  \sum_{C\in\compl} |C|y_C  && \\
\forall S\ni r: \sum_{e\in\delta(S)} x_e &\geq& \min\{1, \sum_{C\subseteq V-S, C\in\compl} y_C\}\\
\sum_e x_e &\leq& k\\
\sum_{C\in\compl} y_C &\geq& 1\\
x_e, y_C &\in& [0, 1]
\end{eqnarray}

\begin{lemma}
\label{lemma:lp-approx}
There exists $\ell\in\{1,\ldots,\log{n}\}$ such that the objective value of $LP_1^{(\ell)}$ is at least $OPT/\log{n}$.
\end{lemma}
\begin{proof}
Consider the following IP:
\begin{eqnarray*}
\nonumber
\max  \sum_{C\in\comp} |C|y_C  && \\
\forall S\ni r: \sum_{e\in\delta(S)} x_e &\geq& \min\{1, \sum_{C\subseteq V-S, C\in\comp} y_C\}\\
\sum_e x_e &\leq& k\\
\sum_C y_C &\geq& 1\\
x_e, y_C &\in& \{0, 1\}
\end{eqnarray*}

The above program is feasible. Let $x^*, y^*$ be an optimal integral solution to the above IP.
Then, $\sum_C |C|y^*_C\geq OPT$.

Next, $\sum_{C\in\comp} |C|y^*_C=\sum_{\ell}\sum_{C\in\compl} |C|y^*_C$. Therefore, there exists $\ell$ such that
$\sum_{C\in\compl} |C|y^*_C\geq OPT/\log{n}$. Futher, there exists $C\in\compl$ such that $y^*_C=1$
(else $\sum_{C\in\compl} |C|y^*_C=0$).


Consider a fractional solution $x, \hat{y}$ such that $\hat{y}_C=y^*_C$ for $C\in\compl$, and 
$\hat{y}_C=0$ for all $C\not\in\compl$. Then, $x, \hat{y}$ is a feasible solution to $LP_1^{(\ell)}$.
Therefore, the lemma follows.
\end{proof}

For a set of components $D=\{C_1,\ldots,C_r\}\subseteq\compl$, define $\Gamma(D)=\bigcup_{C\in D} C$ to be the union of the sets $C$ in $D$, and let $y_D=\sum_{C\in D} y_C$.

\begin{lemma}
\textcolor{red}{Suppose $\einf(T^*, G)\geq \frac{2}{1-\epsilon}\log{n}$. Then, with high probability, there exists $\ell$ such that $OPT^{(\ell)}\geq 1$ and in the program $LP_1^{(\ell)}$, we have $\sum_{C\in\compl} y_C\geq 1$. **** NOT RIGHT}
\end{lemma}
\begin{proof}
\textcolor{red}{By Lemma \ref{lemma:conc}, we have $\sinf(T^*, \G)\geq (1-\epsilon)\einf(T^*, G)$, with high probability. Since $\sum_{\ell} 2OPT^{(\ell)}\geq OPT=\sinf(\hat{T},\G)\geq\sinf(T^*,\G)$, there exists $\ell$ such that $OPT^{(\ell)}\geq 1$.}
\end{proof}

\begin{lemma}
\label{lemma:supergrp}
%Suppose $\einf(T^*, G)\geq \frac{2}{1-\epsilon}\log{n}$. 
Suppose $OPT=\Omega(\log{n})$ and $\sum_{C\in\compl} y_C\geq 1$.
Then, with high probability, it is possible to construct a partition $\mathcal{D}=\{D_1,\ldots,D_M\}$ of a subset of $\compl$ such that:
(1) for all $D\in\mathcal{D}$, we have $y_D=\sum_{C\in D} y_C \in[1/2, 1]$,
(2) $\sum_{D\in\mathcal{D}} y_D \geq \frac{1}{2}\sum_{C\in\compl} y_C$,
(3) for all $S\subseteq V$ with $r\in S$, such that $\Gamma(D) \subseteq V-S$ for some $D\in\mathcal{D}$,
we have $\sum_{e\in\delta(S)} x_e\geq 1/2$, 
(4) $\sum_e x_e\leq k$, and
(5) $2^{\ell}M\geq OPT/(2\log{n})$.
\end{lemma}
\begin{proof}
Let $\compl=\{C_1,\ldots,C_{N_{\ell}}\}$. We arbitrarily partition $C_1,\ldots,C_{N_{\ell}}$ into $M+1\geq 2$ groups
$$D_1=\{C_1,\ldots,C_{i_1},\}, D_2=\{C_{i_1+1},\ldots,C_{i_2}\},\cdots,D_M=\{C_{i_M-1},\ldots,C_{i_M}\}, D_{M+1}=\{C_{i_M+1},\ldots, C_{i_{N_{\ell}}}\}$$ 
such that:
$y_{D_j}=\sum_{C\in D_j} y_{C}\in[1/2, 1]$ for all $j=1,\ldots,M$, and $y_{D_{M+1}}< 1/2$ (note: group $M+1$ can be empty).

We have $\sum_{j=1}^M y_{D_j}\geq \sum_{C\in\compl} y_C - y_{D_{M+1}} \geq \sum_{C\in\compl} y_C - 1/2 \geq \frac{1}{2}\sum_{C\in\compl} y_C$,
since $\sum_{C\in\compl} y_C\geq 1$. 

Consider any $S\subseteq V$ with $r\in S$, such that $\Gamma(D)\subseteq V-S$ for some $D\in\mathcal{D}$,
we have 
\[
\sum_{e\in\delta(S)} x_e \geq \min\{1, \sum_{C\in\compl, C\subseteq V-S} y_C\}
\geq \min\{1, \sum_{C\in D} y_C\}\geq 1/2
\]
Therefore, the lemma follows.
\end{proof}

\noindent
\textbf{Our algorithm.}
\begin{enumerate}
\item
Guess $\ell$, and find a fractional solution $x$ and a partition $D$ of $\compl$ such that
(1) for all $S\subseteq V$ with $r\in S$, such that $\Gamma(D) \subseteq V-S$ for some $D\in\mathcal{D}$,
we have $\sum_{e\in\delta(S)} x_e\geq 1/2$, 
(2) $\sum_{D\in\mathcal{D}} y_D \geq \frac{1}{2}\sum_{C\in\compl} y_C$,
(3) $\sum_e x_e\leq k$, and
(4) $2^{\ell}M\geq OPT/(2\log{n})$.
We refer to such a solution as a ``good'' solution
\item
Consider a group steiner tree problem on $G$ with a group $g_D=\cup_{C\in D} C$ corresponding to each 
$D\in\mathcal{D}$; let $\mathcal{G}=\{g_D: D\in\mathcal{D}\}$ be the set of all groups.
Construct tree $T$ by using the Garg et al. algorithm for rounding $x$
\end{enumerate}

\begin{lemma}
The tree $T$ computed by the above rounding algorithm ensures that $|T|=O(k\log^c{n})$, and
$\sum_{C\in\comp, C\cap T\neq\phi} |C|\geq OPT/(2\log{n})$, with high probability.
\end{lemma}
\begin{proof}
The rounding algorithm of Garg et al. guarantees that (1) $|T|=O(k\log^c{n})$, and (2) for each $g_D$,
there exists a node $v\in g_D$ such that $v\in T$.
This implies, there exists $C\in D$ with $C\cap T\neq\phi$.
Further, $|C|\in[2^{\ell}, 2^{\ell+1})$ for each $C\in D$.
Therefore, we have 
\[
\sum_{C\cap T\neq\phi} |C| \geq \sum_{D\in\mathcal{D}} 2^{\ell}=M2^{\ell}\geq OPT/(2\log{n})
\]
\end{proof}

\noindent
\textbf{Finding a ``good'' solution.}
We use the ellipsoid method. We solve $LP_1^{(\ell)}$ using the following separation oracle,
which takes as input a fractional solution $x, y$ (with the constraint $\sum_{C\in\compl} |C|y_C\geq OPT/\log{n}$)
\begin{enumerate}
\item
Check if the constraints $\sum_{C\in\compl} |C|y_C\geq OPT/\log{n}$ and $\sum_e x_e\leq k$ are violated.
If so, return those.
\item
Partition the set $\compl$ into
$$C_1,\ldots,C_{i_1},C_{i_1+1},\ldots,C_{i_2},\cdots,C_{i_M-1},\ldots,C_{i_M=N_{\ell}}$$ such that:
$\sum_{j=i_p}^{i_{p+1}} y_{C_{i_j}}\in[1/2, 1]$ for all $p=0,\ldots,M-1$.
\item
For each $p=0,\ldots,M-1$, compute the total flow from $D_p=\cup_{j=i_p}^{i_{p+1}} C_{i_j}$ to the root $r$,
using the $x_e$ values as capacities. If the total flow is less than 
$\sum_{j=i_p}^{i_{p+1}} y_{C_{i_j}}$, the minimum cut $(V-S, S)$ gives a violated constraint
\end{enumerate}


\section{Submodular function maximization with connectivity constraints}

\noindent
\textbf{Problem.}
Given a graph $G=(V, E)$, a non-negative monotone submodular function $f:V\rightarrow\mathbb{R}$, and a parameter $k$, the goal is to find a connected subset $S\subset V$ such that $|S|\leq k$, such that $f(S)$ is maximized.

\begin{itemize}
\item 
The recursive greedy algorithm for the orienteering problem \cite{Chekuri:2005:RGA:1097112.1097461} gives an $O(\log{OPT})$ approximation in  $O(n^{O(\log{n})})$ time.
\end{itemize}